Back to Normal Transits for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-06 ms.tex
a few more text updates for the note.

\section{Abstract}
KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface. Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of integration activity in 2013 and 2014. Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
We also examine the system with high resolution spectroscopy and discuss the parameters of the host star.

@@

Subsequently, \citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
\citet{schlawin2016kic1255} found that the transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
This was evidence that the observations occurred during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
We performed follow-up $R$ band photometry of the \shStar\ system to explore whether the disintegration activity was decreasing as a function of time.
We also analyze high resolution spectroscopy of the system to help resolve some of the different stellar parameters reported in the literature.

@@

Figure \ref{fig:allNightrefCorrect} shows the reference-corrected time series for \shStar\ showing transits.
We use the following planet transit ephemeris, using the flux minimum from Kepler data \citep{schlawin2016kic1255} and the orbital period from \citet{vanWerkhoven2014}.
\begin{equation}
T = T_0 + n P
\end{equation}
where $T_0 = 2454833.039$ BJD$_{TDB}$ and $P = 0.653 553 8 \pm 0.000 000 1$ days.

>>>>

\section{Abstract}
KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface. Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of integration activity in 2013 and 2014. Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.

@@

Subsequently, \citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
\citet{schlawin2016kic1255} found that the transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
This was evidence that the observations occurred during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
We performed follow-up $R$ band photometry of the \shStar\ system to explore the second hypothesis: that the disintegration activity decreases as function of time.

@@

Figure \ref{fig:allNightrefCorrect} shows the reference-corrected time series for \shStar\ for all 5 nights which were timed with transits.
We use the following planet transit ephemeris, using the flux minimum from Kepler data \citep{schlawin2016kic1255} and the orbital period from \citet{vanWerkhoven2014}.
\begin{equation}
T = T_0 + n P
\end{equation}
where $T_0 = 2454833.039$ BJD$_{TDB}$ and $P = 0.653 553 8 \pm 0.000 000 1$ days.
